Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs

### 2020-01-14 main.tex
Update introduction

@@

We also have access to a measurement of the form
$
    \dot{x}(t) + C\nu(t)
$
that we will actually denote (since the control $u(t)$ is known) as:
\begin{equation}
\label{eq:measurement}
    y(t) = \dot{x}(t) - Bu(t) + C\nu(t)
\end{equation}
where $\nu(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known. Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further.

@@

Denote $\eta(t) = C\nu(t) + D\omega(t)$. By simply substituting the expression of $y_n$ into \eqref{eq:vector_rls}, we obtain the regression error:
\begin{align}
    \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - \lambda G_{N, \lambda}^{-1}\theta 
\end{align}

@@

\begin{assumption}[Bounded noise]
\label{assumpt:bounded-noise}
The noise $\eta(t) = C\nu(t) + D\omega(t)$ is bounded.
\[\|\eta\|_\infty < \infty\]
\end{assumption}

Then, 
\begin{align}
\label{eq:bounded-noise-polytope}
\|\theta_{N,\lambda} - \theta\|_1 \leq &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
&+ \lambda\|G_{N, \lambda}^{-1}\|_1\|\theta\|_\infty \nonumber
\end{align}

This $L_1$-ball is a polytope with $2d$ vertices, denoted $\cP$.

>>>>

Our contributions are the following:
In Section 2, we structured dynamics. In order to derive the confidence regions, we rely on the work of \citet{Abbasi2011} that provide confidence ellipsoid for the regularised least-square estimator. However, we need to extend their result by one dimension, with matricial features and vectorial noise where the original setting involved vectorial features and scalar noise.

@@

We also have access to the observation of $x(t)$ and to noisy a measurement of $\dot{x}(t)$ in the form
$
    \dot{x}(t) + C\nu(t)
$ where $\nu(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known.
For better readability, we will actually denote the measurement as:
\begin{equation}
\label{eq:measurement}
    y(t) = \dot{x}(t) - A_0 x(t) - Bu(t) + C\nu(t)
\end{equation}
which is possible since the nominal dynamics $A_0$, thet state $x(t)$ and the control $u(t)$ are known.
Assumptions over the disturbance $\omega$ and noise $\nu$ will be detailed further, and we denote their total contribution as $\eta(t) = C\nu(t) + D\omega(t)$.

@@

By simply substituting the expression of $y_n$ into \eqref{eq:vector_rls}, we obtain the regression error:
\begin{align}
    \theta_{N,\lambda} - \theta = G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\eta_n - \lambda G_{N, \lambda}^{-1}\theta 
\end{align}

@@

\begin{assumption}[Bounded noise]
\label{assumpt:bounded-noise}
The noise $\eta(t)$ is bounded.
\[\|\eta\|_\infty < \infty\]
\end{assumption}

With Hölder inequality, we obtain a confidence region $\cC$ defined by a $L_1$-ball, i.e. a polytope with $2d$ vertices:
\begin{equation}
\begin{split}
\label{eq:bounded-noise-polytope}
\|\theta_{N,\lambda} - \theta\|_1 \leq {} &\|G_{N, \lambda}^{-1}\sum_{n=1}^N \Phi_n^\transp \Sigma_p^{-1}\|_1\|\eta\|_\infty \\
&+ \lambda\|G_{N, \lambda}^{-1}\|_1\|\theta\|_\infty
\end{split}
\end{equation}
